opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-11-22 chapters/02_existing_datasets.tex
Overhauled PDF entry in existing datasets

% Datset listing (List written on 20.06.24)
% Some other Lists of Crystallographic databases
% - IUCR: "Crystallographic databases and related resources" (https://www.iucr.org/resources/data/databases)
% - Bruno et al. (2017): "Crystallography and Databases" (https://datascience.codata.org/articles/10.5334/dsj-2017-038)
% - University of Virginia "Crystallographic data" (https://guides.lib.virginia.edu/c.php?g=514782&p=3568808)

@@

\begin{itemize}
\item \textbf{Powder Diffraction File:} \footnote{More information on the Powder Diffraction File can be found under \url{https://www.icdd.com/pdf-5/}.} The Powder Diffraction File (PDF), published and maintained by the International Center for diffraction data, is currently the largest collection of powder diffraction data available to researchers. Though its latest release contains over a million entries, almost all are simulated patterns. Only 19000 entries represent powder diffraction data originating from experiments, and of those, only about 11000 come with accompanying atomic coordinates. It is widely used as a reference database in Rietveld refinement to identify crystal structures from which the refinement process can begin based on their powder diffraction patterns. As of November 2024, the latest release of the PDF, the PDF5+, is available to researchers through a purchase starting at a price point of \$6,265.00.

@@

\item Scattered experimental datasets on Zenodo (TODO: roughly estimate size)

>>>>

% Datset listing (List written on 20.06.24)
% Lists of Crystallographic databases; Our list contains all of the databases given in the lists linked below
% - IUCR: "Crystallographic databases and related resources" (https://www.iucr.org/resources/data/databases)
% - Bruno et al. (2017): "Crystallography and Databases" (https://datascience.codata.org/articles/10.5334/dsj-2017-038)
% - University of Virginia "Crystallographic data" (https://guides.lib.virginia.edu/c.php?g=514782&p=3568808)

@@

\begin{itemize}
\item \textbf{Powder Diffraction File:} \footnote{More information on the Powder Diffraction File can be found under \url{https://www.icdd.com/pdf-5/}.} The Powder Diffraction File (PDF), published and maintained by the International Center for Diffraction Data (ICDD), is a large collection of materials with accompanying powder diffraction data. Its latest release as of November 2024, the PDF5+, contains over a million materials with accompanying powder diffraction data. However, most of these powder diffraction patterns are simulated. After inquiring with the ICDD in April 2024 we were told that only 19000 of the powder diffraction patterns in the PDF5+ stemmed from experiments. \footnote{We reached out to the contact address given on their website, info@icdd.com.} Still, this makes the PDF5+, to the best of our knowledge, the largest collection of experimental powder diffraction data available to researchers. As of November 2024, the latest release of the PDF, the PDF5+, is available to researchers through a purchase starting at a price point of \$6,265.00.

@@
